DMRGenie: Graphical interface for entanglement renormalization

### 2024-12-29 paper/header.tex
Add files via upload

\title{DMRGenie: Fully graphical user interface for entanglement renormalization}

\author[1]{Kiana Gallagher}
\author[1]{Aaron Dayton}
\author[2]{Drew Leske}
\author[2]{Sarah Huber}
\author[1,3,4]{Thomas E.~Baker}
\affil[1]{Department of Physics \& Astronomy, University of Victoria, Victoria, British Columbia V8P 5C2, Canada}
\affil[2]{Research Computing Services, University of Victoria, Victoria, British Columbia V8P 5C2, Canada}
\affil[3]{Department of Chemistry, University of Victoria, Victoria, British Columbia V8P 5C2, Canada}
\affil[4]{Centre for Advanced Materials and Related Technologies, University of Victoria, Victoria, British Columbia V8P 5C2, Canada}

\keywords{Julia, Entanglement Renormalization, Tensor Networks}

\hypersetup{
pdftitle = {My JuliaCon proceeding},
pdfsubject = {JuliaCon 2019 Proceedings},
pdfauthor = {1st author, 2nd author, 3rd author},
pdfkeywords = {Julia, Optimization, Game theory, Compiler},
}

>>>>

\title{DMRGenie: Graphical interface for entanglement renormalization}

\author[1]{Kiana Gallagher}
\author[1]{Aaron Dayton}
\author[2]{Drew Leske}
\author[2]{Sarah Huber}
\author[134]{Thomas E. Baker}
\affil[1]{Department of Physics \& Astronomy, University of Victoria, Victoria, British Columbia V8P 5C2, Canada}
\affil[2]{Research Computing Services, University of Victoria, Victoria, British Columbia V8P 5C2, Canada}
\affil[3]{Department of Chemistry, University of Victoria, Victoria, British Columbia V8P 5C2, Canada}
\affil[4]{Centre for Advanced Materials and Related Technologies, University of Victoria, Victoria, British Columbia V8P 5C2, Canada}

\keywords{Julia, Genie, DMRjulia, TENPACK, Entanglement Renormalization, Tensor Networks, Graphical User Interface}

\hypersetup{
pdftitle = {DMRGenie: Graphical interface for entanglement renormalization},
pdfsubject = {JuliaCon 2022 Proceedings},
pdfauthor = {Kiana Gallagher, Aaron Dayton, Drew Leske, Sarah Huber, Thomas E. Baker},
pdfkeywords = {Julia, Genie, DMRjulia, TENPACK, Entanglement Renormalization, Tensor Networks, Graphical User Interface},
}
